Efficient Compilation of High Level Python Numerical Programs with Pythran

### 2014-09-04 doc/papers/cgo2014/paper.tex
Add a small snippet concerning the full benchmark

@@

    \centering{
\begin{tabular}{|l||c|c|c|c|c|}
\hline
& Python & numba & parakeet & pypy & pythran \\
\hline
\hline
       allpairs\_distances &   37727 &             0 &          1768 &         36855 & \textbf{1079} \\
allpairs\_distances\_loops &   49799 &         55867 &          1781 &         50253 & \textbf{1758} \\
             arc\_distance &    1365 &          1401 &          1596 &          1364 &  \textbf{494} \\
                      conv & 1926454 &       2356675 &          2032 &       1899006 & \textbf{1944} \\
              create\_grid &    3867 &          3950 &             0 & \textbf{3833} &          5512 \\
                  cronbach &    1637 &          1681 &             0 &          1756 & \textbf{1136} \\
                 diffusion &   22511 &         23564 &         21167 &         22450 & \textbf{9606} \\
                    evolve &    5762 &             0 &             0 &          5522 & \textbf{3841} \\
                      fdtd & 1558799 &       1824395 &             0 &       1538692 & \textbf{1198} \\
                       fft &   25720 &             0 &             0 &         24771 & \textbf{1211} \\
                  grouping &    2095 &             0 &             0 &          2104 &  \textbf{839} \\
                   growcut & 1807849 &          5573 & \textbf{2200} &       1860926 &          3930 \\
                    harris &    5516 &          5258 &          5084 &          5500 & \textbf{2994} \\
                   hyantes &  259268 &             0 & \textbf{1865} &        261074 &          2359 \\
                     julia & 2716770 &          2716 &          2930 &       2776183 & \textbf{2636} \\
                    l2norm &    6057 &          6008 &         12574 &          6069 &  \textbf{540} \\
             local\_maxima &   59822 &             0 &             0 &         60504 & \textbf{5084} \\
                    lstsqr &    7886 &          8652 &             0 &          7891 & \textbf{1680} \\
                    mandel &  437908 & \textbf{4361} &             0 &        439827 &          5075 \\
             multiple\_sum &    2981 &          3194 &          8206 &          2975 & \textbf{2007} \\
                  pairwise & 3888235 &          5777 &          3699 &       3873927 & \textbf{3435} \\
            periodic\_dist &    1848 &          1983 &             0 &          1863 &  \textbf{951} \\
                 repeating &    1216 &          1228 &             0 &          1226 &  \textbf{568} \\
           reverse\_cumsum &    2620 &          2629 &             0 &          2614 & \textbf{2389} \\
                     rosen &   14693 &         19419 &          1557 &         14611 &  \textbf{894} \\
                 slowparts &    5687 &             0 & \textbf{1223} &          5900 &          1537 \\
                 smoothing &  911126 & \textbf{4858} &          6258 &        935202 &          4924 \\
           specialconvolve &    8211 &          6665 &         10340 &          8140 & \textbf{2449} \\
              vibr\_energy &    2563 &          2450 &          2488 &          2548 & \textbf{1112} \\
                      wave &   54234 &         54529 &             0 &         51471 & \textbf{1886} \\
                     wdist &   82669 &         90274 & \textbf{1457} &         80406 &          1469 \\
\hline
\end{tabular}
}
\caption{Average execution times for all kernels of the numpy-benchamrks.}
\end{table*}

>>>>

Table~\ref{tbl:overview} presents the average execution time for each kernel
and each compiler, with the lowest values highlighted in
bold font. Zeros are used when the given compiler failed to
compile the kernel. Concerning the Numba compiler, this
benchmarks conﬁrms that it works best on explicit loops. It
gives non performance gain when run on high-level kernels,
either falling back to the generation of calls to Python C
API, or stopping compilation. PyPy is the most robust of
the compilers, but to a few exceptions, it does not generate
code more efﬁcient than the original version. This reﬂects
the fact that Numpy support is still a work-in-progress task.
Parakeet performs extremely well on high-level benchmarks.
Although it does not supports some Numpy constructs, it
successfully parallelize many of them, and also generates
efﬁcient code for explicit loops. Pythran still performs better
than Parakeet on some kernels, whenever it successfully
vectorizes operations.

    \centering{
\begin{tabular}{|l||c|c|c|c|c|}
\hline
& Python & numba & parakeet & pypy & pythran \\
\hline
\hline
       allpairs\_distances &   37727 &             0 &          1768 &         36855 & \textbf{1079} \\
allpairs\_distances\_loops &   49799 &         55867 &          1781 &         50253 & \textbf{1758} \\
             arc\_distance &    1365 &          1401 &          1596 &          1364 &  \textbf{494} \\
                      conv & 1926454 &       2356675 &          2032 &       1899006 & \textbf{1944} \\
              create\_grid &    3867 &          3950 &             0 & \textbf{3833} &          5512 \\
                  cronbach &    1637 &          1681 &             0 &          1756 & \textbf{1136} \\
                 diffusion &   22511 &         23564 &         21167 &         22450 & \textbf{9606} \\
                    evolve &    5762 &             0 &             0 &          5522 & \textbf{3841} \\
                      fdtd & 1558799 &       1824395 &             0 &       1538692 & \textbf{1198} \\
                       fft &   25720 &             0 &             0 &         24771 & \textbf{1211} \\
                  grouping &    2095 &             0 &             0 &          2104 &  \textbf{839} \\
                   growcut & 1807849 &          5573 & \textbf{2200} &       1860926 &          3930 \\
                    harris &    5516 &          5258 &          5084 &          5500 & \textbf{2994} \\
                   hyantes &  259268 &             0 & \textbf{1865} &        261074 &          2359 \\
                     julia & 2716770 &          2716 &          2930 &       2776183 & \textbf{2636} \\
                    l2norm &    6057 &          6008 &         12574 &          6069 &  \textbf{540} \\
             local\_maxima &   59822 &             0 &             0 &         60504 & \textbf{5084} \\
                    lstsqr &    7886 &          8652 &             0 &          7891 & \textbf{1680} \\
                    mandel &  437908 & \textbf{4361} &             0 &        439827 &          5075 \\
             multiple\_sum &    2981 &          3194 &          8206 &          2975 & \textbf{2007} \\
                  pairwise & 3888235 &          5777 &          3699 &       3873927 & \textbf{3435} \\
            periodic\_dist &    1848 &          1983 &             0 &          1863 &  \textbf{951} \\
                 repeating &    1216 &          1228 &             0 &          1226 &  \textbf{568} \\
           reverse\_cumsum &    2620 &          2629 &             0 &          2614 & \textbf{2389} \\
                     rosen &   14693 &         19419 &          1557 &         14611 &  \textbf{894} \\
                 slowparts &    5687 &             0 & \textbf{1223} &          5900 &          1537 \\
                 smoothing &  911126 & \textbf{4858} &          6258 &        935202 &          4924 \\
           specialconvolve &    8211 &          6665 &         10340 &          8140 & \textbf{2449} \\
              vibr\_energy &    2563 &          2450 &          2488 &          2548 & \textbf{1112} \\
                      wave &   54234 &         54529 &             0 &         51471 & \textbf{1886} \\
                     wdist &   82669 &         90274 & \textbf{1457} &         80406 &          1469 \\
\hline
\end{tabular}
}
\caption{Average execution times for all kernels of the numpy-benchamrks.}
\label{tbl:overview}
\end{table*}

@@
